%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%   LaTeX source code to approximate a NIST Technical report
%	DOI and CrossMark watermark will be added on final PDF
% 	Developed by K. Miller, kmm5@nist.gov 
%	Last updated: 21-June-2022
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document class and template package DO NOT DELETE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{article}
\usepackage{Style/settings}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DRAFT: TRUE OR FALSE?
% REQUIRED!!! Select either Draft (toggletrue) or Final (togglefalse)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtoggle{draft}
% \toggletrue{draft} % use if this is a Draft
\togglefalse{draft} % use if this is Final

\iftoggle{draft}{
    \usepackage{lineno}
    \linenumbers
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Publication Metadata
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\pubseries}{Series [Technical Note]} % Replace with a series title from the list below %
% {Advanced Manufacturing Series}
% {Data Collection Instruments}
% {Economic Analysis Brief}
% {Grant/Contractor Report}
% {Handbook}
% {IR}
% {Special Publication}
% {Technical Note}
% {Technology Transfer Brief}
% {NCSTAR}
\newcommand{\pubnumber}{Publication Identifier} 
\newcommand{\DOI}{https://doi.org/10.6028/NIST.XXX.XXXX}
\newcommand{\pubmonth}{Month}
\newcommand{\pubyear}{Year}
\newcommand{\erratadate}{MM-DD-YYYY}
\newcommand{\pubtitle}{Efficient Sampling Method to Propagate Uncertainty in Community Resilience System Models}
% \newcommand{\pubsubtitle}{Subtitle} % delete if no subtitle %
% \newcommand{\draftstage}{Draft Stage} % Draft Stage is REQUIRED for drafts/preprints; Draft stages are listed in the NIST Publication Identifier guidance: https://www.nist.gov/nist-research-library/nist-technical-series-publications-author-instructions#pubid   %
\newcommand{\authorlist}{Author 1, Author 2, Author 3}
\newcommand{\authorone}{Author 1}
\newcommand{\authortwo}{Author 2}
\newcommand{\authorthree}{Author 3}

\newcommand{\pubabstract}{Resilience analysis of complex systems often involves uncertainty due to factors such as material randomness, demand and structural strength variations, infrastructure failures, dynamic environmental features, and human factors. Uncertainty propagation, a technique to study the impact of uncertain factors on models, involves quantifying output uncertainty resulting from input uncertainty. Monte Carlo (MC) simulation is a popular technique for uncertainty propagation, but its sampling error may affect the reliability of rare event estimates. Importance sampling is a variance reduction technique that can estimate quantities accurately with fewer samples. In this paper, we compare the computational performance of Monte Carlo and importance sampling methods for the reliability analysis of a water distribution network. Specifically, we demonstrate the application of an adaptive importance sampling technique, Markov-Chain Monte Carlo Importance Sampling (MCMC-IS), in comparison with crude Monte Carlo. Our results show that MCMC-IS outperforms crude Monte Carlo in estimating small failure probabilities with fewer samples. This paper provides a valuable resource for resilience analysts and risk assessors who want to use importance sampling to improve the effectiveness of probability of failure estimation.}
\newcommand{\keywords}{Uncertainty propagation; importance sampling; Monte Carlo; Markov chain Monte Carlo.}
\newcommand{\publang}{English} %If translation, change to correct language%

\usepackage{Style/pdfproperties}
